\documentclass[10pt]{article}

\usepackage[shortlabels]{enumitem}

\usepackage{geometry}
\geometry{a4paper,tmargin=1in,bmargin=1in,lmargin=1.4in,rmargin=1.4in}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
    urlcolor=blue,
}

\begin{document}

\title{Human Resources Document -- Staff Code of Conduct}

\textsc{Effective date: 3 April 2023}

\section{Introduction}
\begin{enumerate}[(a)]
	\item Valor is customer-obsessed and know that deivering the best possible experiences to everyone.

	\item You should not engage in behaviour that jeapordises the ability of yourself or Valor to deliver high-quality experiences.
\end{enumerate}


\section{Interpretation}
\begin{enumerate}[(a)]
	\item
	In this Staff Code of Conduct, unless a contrary intention appears:
	\begin{itemize}
		\item[]
		\textbf{person} and words importing \textbf{persons} includes partnerships, associations, corporations, and companies.

		\item[]
		\textbf{Valor} means Valor Esports Pty Ltd ABN 94 648 832 080 and its subsidiaries (if any).

		\item[]
		\textbf{Valor Admin Team} means the co-founders of Valor, being \textit{Louk Issa, Sam Ward, and Nick Schlobohm}.

		\item[]
		\textbf{in writing} or \textbf{written} means printing, typewriting, and all other means of representing or reproducing words in visible form, including handwriting.
	\end{itemize}

	\item
	Words importing the singular include the plural and vice versa. Words importing the masculine include the feminine and the neuter and vice versa.

	\item
	Headings are for ease of reference only and do not affect the meaning of this Code of Conduct.
\end{enumerate}


\section{External work}
You may undertake external work, so long as:
\begin{enumerate}[(a)]
	\item your external work does not materially impact your Valor obligations; and
	\item you do not `poach' Valor clients/customers for your external work.
\end{enumerate}


\section{Coaching sessions}
\subsection{Session requirements}
When running live coaching sessions, you must ensure that you always follow the ``coaching session requirements'' which are \href{https://valoresports.github.io/coach-resources/docs/live-coaching/live-coaching-session-requirements}{clearly documented on the Valor Coach Resources website}.

\subsection{Failing to attend a session}
\begin{enumerate}[(a)]
	\item If you fail to attend a live coaching session, we have a three-strike policy. If you fail to attend three~(3) live coaching sessions within a three-month period, you will be suspended from coaching live sessions. We will find alternative coaching for the player(s) you coach, and instead find other ways to work with you.

	\item If you are ten~(10) or more minutes late to a live coaching session, this counts as failing to attend the live coaching session.
\end{enumerate}

\section{Communications}
\begin{enumerate}[(a)]
	\item Do not engage in \textbf{any} unobserved one-on-one activity with a Valor player, regardless of their age. This includes communicating with the player via a private messaging system on Discord or any other platform. You must only talk to players through the public channels in our Discord server.

	\itshape
	NOTE: If a player reaches out to you personally with a serious issue (for example, mental health concerns), please talk to the Valor Admin Team. We have strong and confidential processes in place to assist all players.
	\normalshape

	\item At Valor, we do not tolerate harmful or abusive behaviour at any level. You should not act harmfully towards anybody at Valor (including players). Further, as a staff member, you also should not tolerate harmful or abusive behaviours from (or between) players.

	\item Adopt responsible behaviour in relation to alcohol and other drugs. It goes without saying that you should not attend a meeting or a live coaching session when under the influence of drugs.

	\item Ensure your decisions and actions contribute to a harassment-free environment at all times.
	\normalshape
\end{enumerate}

\end{document}
