\documentclass[10pt]{article}

\usepackage[shortlabels]{enumitem}

\usepackage{geometry}
\geometry{a4paper,tmargin=1in,bmargin=1in,lmargin=1.4in,rmargin=1.4in}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
    urlcolor=blue,
}

\usepackage[linewidth=1pt]{mdframed}

\begin{document}

\title{Valor Esports -- Responsible Sourcing and Modern Slavery Policy}

\textsc{Effective date: 7 March 2024} \\


\section{Policy}
\label{policy}
Valor is a company that focuses on building a training platform for gamers. Our platform uses proven sport training frameworks to provide players with the best possible training experience. \\

We are committed to ensuring that all of our operations are conducted in a responsible, fair, and sustainable manner in line with our core values.

This Responsible Sourcing and Modern Slavery Policy sets out Valor's commitment to the procuring of goods and services, our responsible sourcing, and our expectations of suppliers in this regard. We are committed to developing and maintaining effective working relationships with suppliers that are aligned with Valor's core values, ethical business principles, and our commitment to sustainability and corporate responsibility.


\section{Principles}
\label{principles}
The over-arching principle of responsible sourcing is to reduce the risk of illegal and human rights violation risks in our supply chain and procurement process. Ethicality in the supply chain and procurement process relates to Valor taking all reasonable steps to ensure no breach of local or international legislation such as the \textit{Modern Slavery Act 2018 (Cth)} (the \textbf{Act}) has occurred during the entire life cycle of the product or service purchased.

We uphold the following principles, and expect the same of our suppliers:
\begin{enumerate}[(1)]
	\item create a safe workplace for all of its employees, contractors and the broader community;
	\item respect and promote human rights and commit to eliminating any human rights harm and any form of modern slavery from within its supply chain;
	\item uphold strong ethics with business conducted lawfully without bribery, corruption, or any type of fraudulent behaviour;
	\item act responsibly to minimise the impacts of its business and its supply chain to the environment and the community; and
	\item acknowledging and respecting indigenous cultures, particularly Aboriginal and Torres Strait Islander cultures.
\end{enumerate}

Additionally, we are committed to environmental responsibility and minimising the impact of our business on the environment and the communities in which we operate. Suppliers are similarly expected to work toward improving their own environmental performance and minimising any negative environmental impacts associated with their businesses.


\section{Supplier Responsibilities}
\label{supplierresponsibilities}

Suppliers are expected to have read, understood and act consistently with this Policy, which will be made available to parties involved in potentially relevant procurement processes and supply-related contracts or agreements. Valor's suppliers are expected to communicate the aims and expectations of this Responsible Sourcing and Modern Slavery Policy to their own supply chain when supplying products or services connected to the Group.

We expect our suppliers to:
\begin{enumerate}[(1)]
	\item collaborate with Valor to manage any modern slavery risks within their supply chains, including implementing measures to assess, minimise, and address modern slavery risks and encourage greater sourcing transparency;
	\item take all reasonable steps to source labour, products, services, and materials from sources free of modern slavery and that reduce environmental impacts;
	\item establish a mechanism accessible to all workers for them to report and resolve concerns and grievances, anonymously and/or without fear of retribution; and
	\item promote the use of diverse supply partners, including Aboriginal and/or Torres Strait Islander businesses, social enterprises, and local businesses wherever possible.
\end{enumerate}

Suppliers are obligated to comply with all laws and regulations relating to environmental compliance, human rights, labour practices, health and safety, business integrity, anti-corruption, and bribery, in the jurisdictions that they operate.


\section{Definitions}
\begin{itemize}
	\item[]	
	\textbf{Valor} means Valor Esports Pty Ltd ABN 94 648 832 080 and its subsidiaries (if any).
\end{itemize}


\end{document}
