\documentclass[10pt]{article}

\usepackage[shortlabels]{enumitem}

\usepackage{geometry}
\geometry{a4paper,tmargin=1in,bmargin=1in,lmargin=1.4in,rmargin=1.4in}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
    urlcolor=blue,
}

\begin{document}

\title{User Agreement -- Valor Training Platform Terms and Conditions}

\textsc{Effective date: 26 February 2023}


\section{Introduction}
These Terms and Conditions (\textbf{Terms}) apply to your access to and use of the websites, emails, and other online products and services (collectively, the \textbf{Services}) provided by Valor Esports Pty Ltd ABN 94 648 832 080 (\textbf{Valor}, \textbf{we}, \textbf{us}, or \textbf{our}).

Valor is a worldwide esports club, and like any good sports club it needs some basic rules. By accessing or using our Services, you agree to be bound by these Terms. If you do not agree to these Terms, you may not access or use our Services.

Please also read \href{https://legal.valoresports.com/academy-policy-privacy-policy.html}{Valor's Privacy Policy} -- it explains how and why we collect, use, and share information about you when you access or use our Services.


\section{Your access to the Services}
Children under the age of 13 are not allowed to create an Account or otherwise use the Services. Additionally, you must be over the age required by the laws of your country to create an account or otherwise use the Services, or we need to have received verifiable consent from your parent or legal guardian.

If you are accepting these Terms on behalf of another legal entity, including a business or government entity, you represent that you have full legal authority to bind such entity to these Terms.


\section{Your use of the Services}
Valor grants you a personal, non-transferable, non-exclusive, revocable, limited licence to use and access the Services solely as permitted by these Terms. We reserve all rights not expressly granted to you by these Terms.

Except as permitted through the Services or as otherwise permitted by us in writing, your license does not include the right to:
\begin{enumerate}[(a)]
	\item
	license, sell, transfer, assign, distribute, host, or otherwise commercially exploit the Services;
	
	\item
	modify, prepare derivative works of, disassemble, decompile, or reverse engineer any part of the Services; or
	
	\item
	access the Services in order to build a similar or competitive website, product, or service.
\end{enumerate}

We reserve the right to modify, suspend, or discontinue the Services (in whole or in part) at any time, with or without notice to you. Any future release, update, or other addition to functionality of the Services will be subject to these Terms, which may be updated from time to time. You agree that we will not be liable to you or to any third party for any modification, suspension, or discontinuation of the Services or any part thereof.


\section{Your Valor Account and Account security}
To use certain features of our Services, you may be required to create a Valor account (an \textbf{Account}) and provide us with a username, password, and certain other information about yourself as set forth in our Privacy Policy.

Valor may collect Personal Information for the primary purpose of providing services and/or products, providing information to clients, and marketing. Valor may also use Personal Information for secondary purposes closely related to the primary purpose, in circumstances where one would reasonably expect such use or disclosure.

You are solely responsible for the information associated with your Account and anything that happens related to your Account. You must maintain the security of your Account and immediately notify Valor if you discover or suspect that someone has accessed your Account without your permission. We recommend that you use a strong password that is used only with your Account.

You will not license, sell, or transfer your Account without our prior written approval.


\section{Third-Party Content and advertisements}
The Services may contain links to third-party websites, products, or services, which may be posted by advertisers, our affiliates, our partners, or other users (\textbf{Third-Party Content}). Third-Party Content is not under our control, and we are not responsible for any third party's websites, products, or services. Your use of Third-Party Content is at your own risk and you should make any investigation you feel necessary before proceeding with any transaction in connection with such Third-Party Content.

The Services may also contain sponsored Third-Party Content or advertisements. The type, degree, and targeting of advertisements are subject to change, and you acknowledge and agree that we may place advertisements in connection with the display of any information on the Services.


\section{Things you cannot do}
\label{sec:things-you-cannot-do}
When using or accessing Valor's website or the Services, you must comply with these Terms and all applicable laws, rules, and regulations. In addition, you may not do any of the following:
\begin{enumerate}[(a)]
	\item
	Use the Services in any manner that could interfere with, disable, disrupt, overburden, or otherwise impair the Services.
	
	\item
	Gain access to (or attempt to gain access to) another user's Account or any non-public portions of the Services, including the computer systems or networks connected to or used together with the Services.
	
	\item
	Upload, transmit, or distribute to or through the Services any viruses, worms, malicious code, or other software intended to interfere with the Services, including its security-related features.
	
	\item
	Use the Services to violate applicable law or infringe any person's or entity's intellectual property rights or any other proprietary rights.
	
	\item
	Access, search, or collect data from the Services by any means (automated or otherwise) except as permitted in these Terms or in a separate agreement with Valor. We conditionally grant permission to crawl the Services in accordance with the parameters set forth in our robots.txt file, but scraping the Services without Valor's prior consent is prohibited.
	
	\item
	Use the Services in any manner that we reasonably believe to be an abuse of or fraud on Valor or any payment system.
\end{enumerate}

We encourage you to report conduct that you believe violates these Terms. We also support the responsible reporting of security vulnerabilities. To report a security issue, please email: \href{mailto:contact@valoresports.com}{contact@valoresports.com}.


\section{Paid Services and Payment Information}
There are no fees for the use of some aspects of the Services. However, some services may be available for purchase (\textbf{Paid Services}).

Valor may change the fees or benefits associated with the Paid Services from time to time with reasonable advance notice of material changes; provided, however, that no advance notice will be required for temporary promotions, including temporary reductions in the fees associated with the Paid Services.

You may submit your debit card, credit card, or other payment information (\textbf{Payment Information}) via our Services to purchase the Paid Services. We use third-party service providers to process your Payment Information. If you submit your Payment Information, you agree to pay all costs that you incur, and you give us permission to charge you when payment is due for an amount that includes these costs and any applicable taxes and fees.


\section{Indemnity}
\label{sec:indemnity}
Except to the extent prohibited by law, you agree to defend, indemnify, and hold us, our directors, officers, employees, affiliates, agents, contractors, third-party service providers, and licensors (the \textbf{Valor Entities}) harmless from any claim or demand, including costs and legal fees, made by any third party due to or arising out of (a) your use of the Services, (b) your violation of these Terms, or (c) your violation of applicable laws or regulations.

We reserve the right to control the defence of any matter for which you are required to indemnify us, and you agree to cooperate with our defence of these claims.


\section{Disclaimers}
\label{sec:disclaimers}
The services are provided ``as is'' and ``as available'' without warranties of any kind, either express or implied, including, but not limited to, implied warranties of merchantability, title, fitness for a particular purpose, and non-infringement. Valor Entities do not warrant that the services are accurate, complete, reliable, current, or error free. Valor does not control, endorse, or take responsibility for any content available on or linked to the services or the actions of any third party or user, including coaches. While Valor attempts to make your access to and use of our services safe, we do not represent or warrant that our services or servers are free of viruses or other harmful components.


\section{Limitation of liability}
\label{sec:limitation-of-liability}
In no event and under no theory of liability, including contract, tort, negligence, strict liability, warranty, or otherwise, will the Valor Entities be liable to you for any indirect, consequential, exemplary, incidental, special, or punitive damages, or lost profits arising from or relating to these Terms or the Services, including those arising from or relating to content made available on the Services that is alleged to be defamatory, offensive, or illegal. Access to, and use of, the Services is at your own discretion and risk, and you will be solely responsible for any damage to your device or computer system, or loss of data resulting therefrom. In no event will the aggregate liability of the Valor Entities exceed the greater of one hundred U.S. dollars (\$100) or any amount you paid Valor in the previous six months for the services giving rise to the claim. The limitations of this section will apply to any theory of liability, including those based on warranty, contract, statute, tort (including negligence) or otherwise, and even if the Valor Entities have been advised of the possibility of any such damage, and even if any remedy set forth herein is found to have failed its essential purpose. The foregoing limitation of liability will apply to the fullest extent permitted by law in the applicable jurisdiction.


\section{Governing law}
\label{sec:governing-law}
Any claims arising out of or relating to these Terms or the Services will be governed by the laws of the State of Queensland. All disputes related to these Terms or the Services will be brought solely in the federal or state courts located in the State of Queensland, and you consent to personal jurisdiction in these courts.


\section{Changes to these Terms}
We may make changes to these Terms from time to time. If we make changes, we will post the revised Terms and update the Effective Date above. If the changes, in our sole discretion, are material, we may also notify you by sending an email to the address associated with your Account (if you have chosen to provide an email address) or by otherwise providing notice through our Services. By continuing to access or use the Services on or after the Effective Date of the revised Terms, you agree to be bound by the revised Terms. If you do not agree to the revised Terms, you must stop accessing and using our Services before the changes become effective.


\section{Termination}
\label{sec:termination}
You may terminate these Terms at any time and for any reason by deleting your Account and discontinuing use of all Services. If you stop using the Services without deactivating your Account, your Account may be deactivated due to prolonged inactivity.

We may suspend or terminate your Account, moderator status, or ability to access or use the Services at any time for any or no reason, including for violating these Terms.

The following sections will survive any termination of these Terms or of your Account: \ref{sec:things-you-cannot-do}, \ref{sec:indemnity}, \ref{sec:disclaimers}, \ref{sec:limitation-of-liability}, \ref{sec:governing-law}, \ref{sec:termination}, and \ref{sec:miscellaneous}.


\section{Miscellaneous}
\label{sec:miscellaneous}
These Terms constitute the entire agreement between you and us regarding your access to and use of the Services. Our failure to exercise or enforce any right or provision of these Terms will not operate as a waiver of such right or provision. If any provision of these Terms is, for any reason, held to be illegal, invalid, or unenforceable, the rest of these Terms will remain in effect. You may not assign or transfer any of your rights or obligations under these Terms without our consent. We may freely assign any of our rights and obligations under these Terms.

\end{document}
