\documentclass[10pt]{article}

\usepackage[shortlabels]{enumitem}

\usepackage{geometry}
\geometry{a4paper,tmargin=1in,bmargin=1in,lmargin=1.4in,rmargin=1.4in}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
    urlcolor=blue,
}

\begin{document}

{\Large User Agreement -- Live Coaching Services}

\hrule height .1mm

\vspace{.5cm}

\section{Introduction}

\subsection{What is this document about?}
\begin{enumerate}[(a)]
\item
This agreement sets out the expectations and obligations of You and Us in relation to live coaching services (and related products and services) that We may provide to You.
\end{enumerate}

\subsection{Definitions}
In this agreement:

\begin{itemize}[label={}]
\item
The \textbf{Platform} refers to Our website (\url{https://valoresports.com/}) and Our related software and online services provided on or in connection with our website, as well as the content on our Discord server.

\item
\textbf{We}, \textbf{Us}, \textbf{Our}, or \textbf{Valor} is a reference to Valor Esports Pty Ltd ABN 94 648 832 080, a company incorporated in Australia.
\end{itemize}

\subsection{Interpretation}
\begin{enumerate}[(a)]
\item
If You deal with Us on behalf of a school/university/college, organization, or some other entity that is not an individual, then:
\begin{enumerate}[(1)]
\item
``You'' includes You and that entity; and

\item
You represent and warrant that You are an authorized representative of that entity with the authority to bind that entity to this agreement, and that You agree to this agreement on that entity’s behalf.
\end{enumerate}
\end{enumerate}

\section{What You can expect from Us}
\subsection{Coach and session structure}
\begin{enumerate}[(a)]
\item
Valor live coaching sessions run for ninety~(90) minutes and are run by a professional esports coach who is focused on developing You and Your team into high quality esports competitors.

\item
Your coach will work closely with You to understand Your current strengths, weaknesses, and goals, and determine a path forward.

\item
All live coaching sessions are recorded by coaches for archival purposes. This is to ensure Your safety and to ensure that We continue to provide high quality products and services. We may also use footage for promotional purposes.

\item
Following the end of each live coaching session, Your team will receive a report from Your coach. The report will contain information about Your team's overall health, a coaching summary, and performance data that We (or Your team's coach) judge useful.
\end{enumerate}

\subsection{Feedback mechanisms}
\begin{enumerate}[(a)]
\item
We endeavour to provide services of the highest quality. To achieve this, We have a series of comprehensive processes in place to ensure consistency and quality across all regions and products and services.

\item
If at any point You feel as though the services We provide are not of a high quality, please directly contact Us to discuss resolution pathways.
\end{enumerate}

\section{What We expect from You}
\subsection{Commitment, attendance, and attitude}
\begin{enumerate}[(a)]
\item
We generally operate with the following mantra in mind: ``You get out what you put in''. We (and Our staff, whether coaches or otherwise) expect You to commit to Your pathway. This includes (but is not limited to):
\begin{enumerate}[(1)]
\item
applying a reasonable amount of effort towards achieving Your goals;

\item
attending scheduled live coaching sessions; and

\item
training/practising outside of live coaching sessions.
\end{enumerate}

\item
You should ensure Your whole team is present for a live coaching session. A session credit will be used for each live coaching session, regardless of whether the full team is present.

\item
If the number of players joining a live coaching session exceeds the maximum amount of players per session for your selected esports title (please refer to the table below), please directly contact Us as early as possible prior to that live coaching session.

\item
All changes to scheduled live coaching session times (whether initiated by You or Us) shall be done in accordance with Our \textit{Session Cancellation and Rescheduling Policy}.

\begin{tabular}{ |l|c| }
\hline
\textbf{Esports title} & \textbf{Player quota} \\
\hline
Rocket League & 6 \\
\hline
Valorant & 5 \\
\hline
Counter-Strike: Global Offensive & 5 \\
\hline
League of Legends & 5 \\
\hline
\end{tabular}
\end{enumerate}

\subsection{Personal information}
\begin{enumerate}[(a)]
\item
In order to provide You with the best experience possible, We or one of Our coaches may ask you for personal information. Please rest assured that any personal information handled by Us is done in accordance with Our Privacy Policy, which is available on Our website at the following URL: \url{https://valoresports.com/privacy-policy}
\end{enumerate}

\section{Other important information}
\subsection{Refunds}
\begin{enumerate}[(a)]
\item
Except where required by law, fees You pay to us are non-refundable. We may, in Our sole discretion, make an exception to this policy on a case-by-case basis, however We emphasise that this is not standard procedure. Please directly contact Us if you would like to discuss refunds.
\end{enumerate}

\subsection{Intellectual property}
\begin{enumerate}[(a)]
\item
Our Platform and its original content (excluding content provided by users), features, and functionality are and will remain the exclusive property of Us and Our licensors (if any). Our Platform is protected by copyright and other laws of Australia.
\end{enumerate}

\end{document}