\documentclass[10pt]{article}

\usepackage[shortlabels]{enumitem}

\usepackage{geometry}
\geometry{a4paper,tmargin=1in,bmargin=1in,lmargin=1.4in,rmargin=1.4in}

\usepackage{hyperref}
\hypersetup{
	colorlinks=true,
    urlcolor=blue,
}

\usepackage[linewidth=1pt]{mdframed}

\begin{document}

\title{Academy Policy -- Privacy Policy}

\textsc{Effective date: 23 April 2023} \\

\textbf{Your privacy is important to us.}


\section{General}
\label{general}
\subsection{Mission}
Valor is a company that focuses on building a training platform for gamers. Our platform uses proven sport training frameworks to provide players with the best possible training experience. \\

Valor operates a training platform (the \textbf{Application}) enables users to record data regarding their performance, which can be used to reliably track performance. \\

We understand that our customers are concerned about their privacy and the confidentiality and security of their Personal Data. Users will maintain full visibility and control with respect to their Personal Data, which will only be used in accordance with this Privacy Policy.

\subsection{What is ``Personal Data''?}
Valor Esports Pty Ltd ABN 94 648 832 080 (\textbf{Valor}) and its subsidiaries (if any) collects, uses, and stores (\textbf{Processes}) Personal Data in the manner set out in this Privacy Policy. \\

\textbf{Personal Data} means information relating to an identified or identifiable natural person, being a person who can be identified, directly or indirectly, in particular by reference to an identifier such as a name, identification number, location data, online identifiers, or to one or more factors specific to the physical, physiological, genetic, mental, economic, cultural, or social identity of that natural person.

\subsection{Non-EU customers}
\label{general_nonEU}
Your rights regarding the Personal Data that we Process are set out in this Policy. Valor complies with the Australian \textit{Privacy Act 1988} (Cth). \\

If you are in a jurisdiction that has specific laws regarding privacy and we are required to comply with those laws, in addition to the rights in this policy, you will also be afforded all rights under those laws. \\

If for any reason you need to contact us, our contact details are:

\begin{verbatim}
	Privacy Officer
	Valor Esports
	PO Box 1977
	Sunnybank Hills  QLD  4109
	Australia
\end{verbatim}

For privacy issues, please email: \href{mailto:support@valoresports.com}{support@valoresports.com}

\subsection{EU customers}
If you are based in the European Union, or your data is otherwise protected by European Union General Data Protection Regulation (\textbf{GDPR}), we will Process your personal data in accordance with both the GDPR and this Privacy Policy. \\

EU Customers may contact us directly using the above contact information, or alternatively may contact our EU Representative Nick Schlobohm at the following email address: \href{mailto:nick.schlobohm@valoresports.com}{nick.schlobohm@valoresports.com}


\section{Minors}
To access the Application and websites, emails, and other online products and services (collectively, the \textbf{Services}) provided by Valor, you must be at least over the age of thirteen~(13). \\

\begin{mdframed}[leftmargin=10pt,rightmargin=10pt]
\textbf{If you are not legally considered an adult, your parent or guardian must agree to the terms of this Privacy Policy on your behalf. Where your parent or guardian has not provided such consent, you must not access any of our Services.}
\end{mdframed}

If you are a parent or guardian providing consent on behalf of a child, references to ``you'' in this Privacy Policy will, as the context requires, be references to both yourself and the child you are responsible for that will be using our Services.


\section{Basis for collection}
We collect Personal Data in the following circumstances:

\subsection{Contractual services}
Where you have requested that we provide you with our Services, we need to Process your Personal Data to:
\begin{enumerate}[(1)]
	\item enter into our agreement with you; and

	\item deliver to you our services.
\end{enumerate}

\subsection{Legitimate business purposes}
We may also Process your Personal Data (even where it is not related to us entering into an agreement or contract with you) where we consider:
\begin{enumerate}[(1)]
	\item you will not be detrimentally impacted;

	\item you would reasonably expect us to engage in such Processing; and

	\item it is necessary to fulfil our legitimate interests.
\end{enumerate}
This may include, for example, processing your Personal Data to improve our range of Services, or to enable our third party service providers to provide us with such services.

\subsection{Legal compliance}
There are certain situations in which we may be required to Process your Personal Data to comply with a law or Court order.

\subsection{Consent}
In certain circumstances we may request that you specifically consent to our Processing of your Personal Data. Where we do so, we will provide an explanation of the nature of the Processing to which you are consenting. If we have requested your consent, you can withdraw your consent at any time by contacting Valor using the contact information contained in clause~\ref{general_nonEU}.


\section{Anonymity}
Due to the nature of the Services provided by Valor it is impractical for us to deal with you on an anonymous basis.


\section{Purpose and nature of collection}
\subsection{How we collect information}
We collect Personal Data in a variety of ways, including:
\begin{enumerate}[(1)]
	\item through our Application and Website;

	\item through communications that we receive from you (whether electronic or otherwise);

	\item through enquiries you make through our Application or Website;

	\item at events in which we are involved and that you attend;

	\item from third parties that share your Personal Data with us; and

	\item when you otherwise voluntarily provide us with your Personal Data (for example, where you respond to a survey or feedback request).
\end{enumerate}

Where it is reasonable or practical to do so, we will endeavour to only collect Personal Data from you directly. However, in some circumstances because of your use of our Services, we may receive Personal Data relating to you from persons other than you (such as where it is provided by a third party). This information is collected so that we can deliver our contractual services to you, as well as in the pursuance of our legitimate business interests.

\subsection{Nature of information}
\subsubsection{General}
The Personal Data which we collect includes:
\begin{enumerate}[(1)]
	\item your contact information (your username, email address, and potentially your Discord handle);

	\item banking and credit card information;

	\item general information regarding your current abilities relating to esports;

	\item general data relating to your physical activity and fitness, including your history of physical injury and general wellbeing (for example, if you have suffered a break or strain);

	\item your account preferences, opinions and feedback that you provide relating to our Services and how you use our Services;

	\item data logs, which may include information such as your internet protocol address, browser type, browser version, clickstream data, referring URLs, the pages of our Website or Application that you visit, the time spent on any pages of our Website or Application, and other log related information relating to your use of our Services; and

	\item all other information that you provide to us voluntarily and directly, including in any enquiry made to us.
\end{enumerate}

\subsubsection{Website data}
Whenever you visit our Website, our servers automatically record information for statistical purposes about your usage of our Website, such as:
\begin{enumerate}[(1)]
	\item the type of browser used;

	\item the referring URL;

	\item the IP address;

	\item the number and type of pages viewed;

	\item the date and time of visits; and

	\item the exit URL.
\end{enumerate}

This information remains anonymous and we do not link it to your or any other Personal Data, unless at the time of visiting our Website you have logged in to a customer or member account on our Website. Accordingly, if you have not identified yourself on our Website we will not link a record of your usage of our Website to you personally.

\subsubsection{Cookies}
We may utilise ``cookies'' through our Website, which enable us to monitor traffic patterns and to serve you more efficiently if you revisit our Website. A cookie does not identify you personally, but it does identify your computer. You can set your browser to disable cookies or to notify you when you receive a cookie and provide you with an opportunity to either accept or reject it in each instance. If you disable cookies, you may not be able to access certain areas or features on our Website or Application.

\subsubsection{Third party advertisements}
From time to time we will allow third parties, including our authorised service providers, advertising partners and ad networks to serve advertisements on our Website or through our Application. Any information that these third parties collect via cookies is completely anonymous and is non-identifiable. If you provide a third party with information directly, we strongly recommend you first review the privacy policy of the relevant third party.

\subsection{Purposes of collecting Personal Data}
\label{purposes}
Generally, we only use Personal Data for providing, evaluating, improving, personalising and developing our Services, Website and Application. More specifically we use Personal Data to:
\begin{enumerate}[(1)]
	\item enable you to interact with and use our Application and Website; \label{purposesList_START}

	\item provide Services to you through our Application, Website, or directly;

	\item acquire and maintain a membership base for Valor;

	\item undertake industry research and statistical analysis, which may be provided to third parties;

	\item perform internal research and for statistical purposes;

	\item promote and market our Services;

	\item enable us to forward you information or material which you have requested, or we believe may be of interest to you;

	\item improve our Services or the Applications and Website through which our Services can be accessed;

	\item deal with your enquiries; \label{purposesList_END}

	\item prosecute and defend any allegations of wrongdoing or unlawfulness; and

	\item achieve any of the purposes described in clauses~\ref{purposesList_START} to \ref{purposesList_END} above.
\end{enumerate}

\subsection{Ancillary use of data}
Typically, we will only Process Personal Data for the reasons set out in clause~\ref{purposes}. However, in some circumstances, we may use Personal Data for reasons other than those specifically identified above. We will only do so where:
\begin{enumerate}[(1)]
	\item our Processing of your Personal Data is related to one of the reasons set out in clause~\ref{purposes};

	\item you would reasonably expect us to use or disclose the Personal Data for those reasons;

	\item you have consented to our Processing of your Personal Data for some other purpose; or

	\item the use or disclosure of the Personal Data is required or authorised by law, the order of a regulatory authority, or a court or tribunal.
\end{enumerate}


\section{Overseas disclosure}
To provide customer support, perform back office functions, store Personal Data, undertake fraud prevention tasks or to otherwise assist us in providing our Services to you, we may engage staff or third-party service providers that are located in a country other than that in which you are based. \\

We have implemented security measures to protect the security of your Personal Data. However, as with any transfer of data, there are still risks of data breaches. \\

Where you are based in the European Union or your Personal Data is otherwise collected in accordance with the GDPR, you acknowledge that there may be instances where your Personal Data is transferred outside of the European Union and to countries which have not been the subject of an ``adequacy decision'' pursuant to the GDPR. Such transfers are necessary for our legitimate business purposes and in order for us to perform our Services. \\

\begin{mdframed}[leftmargin=10pt,rightmargin=10pt]
\textbf{By requesting our Services you are explicitly consenting to the international transfer and Processing of your Personal Data in accordance with this Privacy Policy, in full and informed knowledge of the risks associated with such transfers and Processing.}
\end{mdframed}


In all other circumstances we will only disclose Personal Data to an Overseas recipient if:
\begin{enumerate}[(1)]
	\item you consent to the transfer; or

	\item the disclosure of the information is required or authorised by law, a regulatory authority, or a court or tribunal order.
\end{enumerate}


\section{Security}
We use industry best practices to protect Personal Data that we hold from:
\begin{enumerate}[(1)]
	\item misuse, interference, and loss; and

	\item unauthorised access, modification, or disclosure.
\end{enumerate}

All staff and third-party providers with access to Personal Data, including third-party data storage providers, are required to comply with appropriate information security industry standards. \\

Although we work to ensure our security systems align with industry best standard, there is always risk associated with the transmission of information via the internet. \\

You acknowledge that we cannot guarantee the security of any data transmission, and as such all data transmissions are entirely at your risk. Once we have received your Personal Data, we will take reasonable steps to use procedures and security features to try to prevent unauthorised access, modification or disclosure.


\section{Data rights and retention}
\subsection{Destruction and erasure of Personal Data}
\begin{enumerate}
	\item We will only retain your Personal Data until we no longer require the information for the purpose for which it was collected (for example, to provide our contractual services to you, or for our legitimate business purposes). Once we no longer require the Personal Data, we will take all reasonable steps to destroy the information, or to ensure the information is deidentified (unless we are required to retain the Personal Data by law, a regulatory authority, or the order of a court or tribunal).

	\item Notwithstanding the above, you have the right to request the erasure of your Personal Data. If you wish to have your Personal Data erased, please let us know and we will take all reasonable steps to destroy or deidentify it, unless we need to keep it to comply with a law, or the order of a regulatory authority, court or tribunal. Where we have provided your Personal Data to a third party, we will take reasonable steps to ensure that party also deletes your Personal Data.
\end{enumerate}

\subsection{Access to Personal Data}
We will provide you with access to the Personal Data held by us in relation to you, except to the extent that denying access is required or authorised by law, a regulatory authority, or a court or tribunal order.

\subsection{Request for access}
To request access to your Personal Data please use the contact information contained in this Privacy Policy. We will respond to your request and either provide you with the Personal Data you have requested, or notify you when we will provide you with your Personal Data. Any Personal Data requested will be provided within 30 days of your request, unless we are unable to provide you with access to the Personal Data because, for example, doing so would breach the law, the ruling of a regulatory authority, or a court or tribunal order. If this is the case we will advise you of the reasons we cannot provide your Personal Data.

\subsection{Use of intermediaries}
If you have requested access to your Personal Data and we are unable to provide you with that access, you may request that, where it is reasonable for us to do so, we engage a mutually agreed intermediary to deal with the Personal Data you have requested and that would allow you sufficient access to your Personal Data to meet your requirements.

\subsection{Costs}
We will not charge for providing an initial copy of your Personal Data. However, we reserve the right to charge for providing additional copies of Personal Data. If we do decide to charge you fees, such fees will not be excessive, and we will notify you of those costs prior to providing you with the Personal Data. We may require anticipated costs to be paid prior to providing you with additional copies of your Personal Data.

\subsection{Data portability}
Insofar as it does not adversely affect the rights and freedoms of others and where you have communicated a request to us:
\begin{enumerate}[(1)]
	\item we will provide you with such Personal Data that we have collected about you in a structured, commonly used, and machine-readable format; or

	\item after receiving your request, where technically feasible, we will transmit your Personal Data directly to another data processor or controller.
\end{enumerate}

\subsection{Correction of Personal Data}
\begin{enumerate}[(1)]
	\item We are obligated to ensure that Personal Data that we are Processing is kept accurate and up to date. Please notify us if any of your Personal Data changes, so that we may update our records. You will also have the ability to update substantially the Personal Data that we hold relating to you via our Application and Website.

	\item If at any time you wish to correct any Personal Data held by us, please contact us using the contact information contained in this Privacy Policy. We will correct your Personal Data to ensure that the information is accurate, up to date, complete, relevant and not misleading. If we advise that we are unable to correct your Personal Data, for example due to a law, order of a regulatory authority, or court or tribunal, we will notify you in this regard.

	\item If we correct Personal Data about you that we previously disclosed to another party, we will take reasonable steps in the circumstances to give that party notification that the Personal Data has been corrected, unless it is impracticable or unlawful to do so.
\end{enumerate}

\subsection{Restriction of Processing}
You may request that we limit or restrict the way we Process your Personal Data. Where we are satisfied grounds for restriction exist, we will only Process your Personal Data:
\begin{enumerate}[(1)]
	\item with your consent;

	\item for the establishment, exercise, or defence of legal claims against us; or

	\item for the protection of the rights of another natural or legal person.
\end{enumerate}


\section{Complaints}
If you believe that we have used or disclosed your Personal Data in a manner which is contrary to this Privacy Policy or otherwise breaches an applicable law, then you should contact us using the contact information in this Privacy Policy. We will happily work with you to address any concerns that you may have. \\

If you are based in the European Union and have a complaint regarding your Personal Data, you may also contact our European Representative using the contact information contained in clause~\ref{general} of this Privacy Policy. \\

Within 30 days of receipt of your complaint we will notify you in writing as to what action we propose to take in relation to your complaint and will provide you with details of what further action you can take if you are not satisfied with our response. \\

You also have the right to lodge a complaint with the relevant supervisory authority in your jurisdiction. If you are unsure who your relevant supervisory authority may be, please contact us so that we may provide you with assistance.


\section{Variations}
Any variations to this Privacy Policy will be published on the Website and available through the Application. \\

Where a customer has created an account through a Valor Application, we will (insofar as practicable) provide notice of the update of this Privacy Policy through the Application.


\section{Definitions}
\begin{itemize}
	\item[]
	\textbf{Application} means any software application made available by Valor to its users, as well as any associated platform through which Services are offered, and as updated from time to time.

	\item[]
	\textbf{Services} means the Application and the websites, emails, and other online products and services operated by Valor.

	\item[]
	\textbf{Website} means the website located at the domain name or as updated by us from time to time.

	\item[]	
	\textbf{Valor} means Valor Esports Pty Ltd ABN 94 648 832 080 and its subsidiaries (if any).
\end{itemize}

\end{document}
